Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2024-10-04 index.Rmd
adding testint phases

```{r eval=FALSE, message=F, include=FALSE}
#OR with rby separate
#shell(cmd="ss") # run SS to windows
# or 
r4ss::run(
  dir = dir1,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)
```

@@

#s9
base.model9 <- SS_output(dir=dir9,
                        covar=T,
                        forecast=T)
```

```{r eval= FALSE, message=F, include=FALSE}
# html
SS_plots(base.model1,
         uncertainty=T,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75,
         minbthresh=0.20, 
         forecast=T)

@@

```{r fig.height=6}
SSplotSelex(base.model01,
            subplots = 1)
SSplotSelex(base.model1,
            subplots = 1)
SSplotSelex(base.model2,
            subplots = 1)
SSplotSelex(base.model3,
            subplots = 1)
SSplotSelex(base.model4,
            subplots = 1)
SSplotSelex(base.model5,
            subplots = 1)
SSplotSelex(base.model6,
            subplots = 1)
SSplotSelex(base.model7,
            subplots = 1)
```
```{r}
SSplotComps(base.model1,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
```

@@

```{r}
SSplotRunstest(base.model1,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

```{r eval=FALSE, fig.width=4, fig.height=5}
SSplotRunstest(base.model01,
               subplots = "len",
               add=T)
SSplotRunstest(base.model1,
               subplots = "len",
               add=T)
SSplotRunstest(base.model2,
               subplots = "len",
               add=T)
SSplotRunstest(base.model3,
               subplots = "len",
               add=T)
SSplotRunstest(base.model4,
               subplots = "len",
               add=T)
SSplotRunstest(base.model5,
               subplots = "len",
               add=T)
SSplotRunstest(base.model6,
               subplots = "len",
               add=T)
SSplotRunstest(base.model7,
               subplots = "len",
               add=T)
```

```{r}
SSplotRunstest(base.model1,
               subplots = "cpue",
               add=T)
```

```{r eval=FALSE}
SSplotRunstest(base.model01,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model2,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model3,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model4,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model5,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model6,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model7,
               subplots = "cpue",
               add=T)
```

```{r eval=FALSE}
SSplotJABBAres(base.model01,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model7,
               subplots = "len",
               add=T)
```

```{r}
SSplotJABBAres(base.model01,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model7,
               subplots = "cpue",
               add=T)
```

@@

```{r eval=FALSE}
#one by one
retro(
    dir = dir1,
    oldsubdir = "",
    newsubdir = "Retrospective",
    years = 0:-5,
    exe = "ss_osx",
    extras = "-nox",
    skipfinished = FALSE)
```

@@

retroSummary <- SSsummarize(retroModelstest)

@@

>>>>

```{r eval=FALSE, message=F, include=FALSE}
#OR with rby separate
#shell(cmd="ss") # run SS to windows
# or 
r4ss::run(
  dir = dirtest,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)
```

@@

#s9
base.model9 <- SS_output(dir=dir9,
                        covar=T,
                        forecast=T)

#stest
base.modeltest <- SS_output(dir=dirtest,
                        covar=T,
                        forecast=T)
```

```{r eval= FALSE, message=F, include=FALSE}
# html
SS_plots(base.modeltest,
         uncertainty=T,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75,
         minbthresh=0.20, 
         forecast=T)

@@

```{r fig.height=6}
SSplotSelex(base.model01,
            subplots = 1)
SSplotSelex(base.model1,
            subplots = 1)
SSplotSelex(base.model2,
            subplots = 1)
SSplotSelex(base.model3,
            subplots = 1)
SSplotSelex(base.model4,
            subplots = 1)
SSplotSelex(base.model5,
            subplots = 1)
SSplotSelex(base.model6,
            subplots = 1)
SSplotSelex(base.model7,
            subplots = 1)
```
```{r}
SSplotComps(base.modeltest,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
```

@@

```{r}
SSplotRunstest(base.modeltest,
               subplots = "len",
               add=T,
               plot = TRUE,
               plotdir = Figs)
```

```{r eval=FALSE, fig.width=4, fig.height=5}
SSplotRunstest(base.model01,
               subplots = "len",
               add=T)
SSplotRunstest(base.model1,
               subplots = "len",
               add=T)
SSplotRunstest(base.model2,
               subplots = "len",
               add=T)
SSplotRunstest(base.model3,
               subplots = "len",
               add=T)
SSplotRunstest(base.model4,
               subplots = "len",
               add=T)
SSplotRunstest(base.model5,
               subplots = "len",
               add=T)
SSplotRunstest(base.model6,
               subplots = "len",
               add=T)
SSplotRunstest(base.modeltest,
               subplots = "len",
               add=T)
```

```{r}
SSplotRunstest(base.modeltest,
               subplots = "cpue",
               add=T)
```

```{r eval=FALSE}
SSplotRunstest(base.model01,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model2,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model3,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model4,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model5,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model6,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.modeltest,
               subplots = "cpue",
               add=T)
```

```{r eval=FALSE}
SSplotJABBAres(base.model01,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "len",
               add=T)
SSplotJABBAres(base.modeltest,
               subplots = "len",
               add=T)
```

```{r}
SSplotJABBAres(base.model01,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.modeltest,
               subplots = "cpue",
               add=T)
```

@@

```{r eval=FALSE}
#one by one
retro(
    dir = dirtest,
    oldsubdir = "",
    newsubdir = "Retrospective",
    years = 0:-4,
    exe = "ss_osx",
    extras = "-nox",
    skipfinished = FALSE)
```

@@

retroSummarytest <- SSsummarize(retroModelstest)

@@

retrotest <- SSplotRetro(retroSummarytest,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
